The Efficient Handling of Guards \\in the Design of RPython's Tracing JIT

### 2012-09-07 talk/vmil2012/paper.tex
another todo
a footnote

The papers does not describe any attempts to share the object entries and scope
entries between different deoptimization safe points. This seems to not be
needed in a method-based JIT compiler, because method-based JITs have fewer
deoptimization points than tracing JITs. Indeed, in the evaluation presented in
the second paper~\cite{kotzmann_run-time_2007} the number of safe points is low
for the benchmarks presented there, between 167 and 1512. The size of the
debugging information in the presented benchmarks is at most about half the
size of the machine code generated.

\bigtodo{for comparison we should add the total number of guards per benchmark to one of the tables}

>>>>

The papers does not describe any attempts to share the object entries and scope
entries between different deoptimization safe points. This seems to not be
needed in a method-based JIT compiler, because method-based JITs have fewer
deoptimization points than tracing JITs. Indeed, in the evaluation presented in
the second paper~\cite{kotzmann_run-time_2007} the number of safe points is low
for the benchmarks presented there, between 167 and 1512.\footnote{The fact
that the density of safe points is low also means that the sharing approaches
of this chapter likely would not work well.} The size of the
debugging information in the presented benchmarks is at most about half the
size of the machine code generated.

\bigtodo{for comparison we should add the total number of guards per benchmark to one of the tables, and maybe also the number of traces}
